---
title: "cowplot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(cowplot)
```

## `theme_cowplot()`
```{r}
ggplot(mpg, aes(x = cty, y = hwy, colour = factor(cyl))) + 
  geom_point(size = 2.5) + 
  theme_cowplot()
```


## `save_plot()`
In particular, the cowplot default theme works nicely in conjunction with the save_plot() function the package provides, such that the output pdfs are nicely formatted and scaled and don’t require any additional parameter fiddling:
```{r}
library(cowplot)
plot.mpg <- ggplot(mpg, aes(x = cty, y = hwy, colour = factor(cyl))) + 
  geom_point(size=2.5) +
  theme_cowplot()
# use save_plot() instead of ggsave() when using cowplot
save_plot("mpg.png", plot.mpg,
          base_aspect_ratio = 1.3 # make room for figure legend
)
```


## `background_grid()`
```{r}
plot.mpg + background_grid(major = "xy", minor = "none")
```

## `theme_get {ggplot2}`
```{r}
theme_set(theme_cowplot())
theme_set(theme_gray()) # switch to default ggplot2 theme for good
```


## `plot_grid`
One limitation of ggplot2 is that it doesn’t make it easy to add labels and other annotations to a plot. ggplot2 strictly separates the plot panel (the part inside the axes) from the rest of the plot, and while it’s generally straightforward to modify one or the other we cannot easily change both. To solve this issue in a generic way, cowplot implements a generic drawing layer on top of ggplot2. In this drawing layer, you can add arbitrary graphical elements on top of a graph.

```{r}
plot.mpg <- ggplot(mpg, aes(x = cty, y = hwy, colour = factor(cyl))) + 
  geom_point(size=2.5) + theme_cowplot()
plot.mpg
```

```{r}
plot.diamonds <- ggplot(diamonds, aes(clarity, fill = cut)) + geom_bar() + theme_cowplot() +
  theme(axis.text.x = element_text(angle=70, vjust=0.5))
plot.diamonds
```

```{r}
plot_grid(plot.mpg, plot.diamonds, labels = c("A", "B"))
```


```{r}
plot_grid(plot.mpg, plot.diamonds, labels = c("A", "B"), align = "h")
```

```{r}
plot_grid(plot.mpg, NULL, NULL, plot.diamonds, labels = c("A", "B", "C", "D"), ncol = 2)
```

```{r}
plot_grid(plot.mpg, plot.diamonds, labels = c("A", "B"), nrow = 2, align = "v")
```

```{r}
plot2by2 <- plot_grid(plot.mpg, NULL, NULL, plot.diamonds,
                      labels=c("A", "B", "C", "D"), ncol = 2)
save_plot("plot2by2.png", plot2by2,
          ncol = 2, # we're saving a grid plot of 2 columns
          nrow = 2, # and 2 rows
          # each individual subplot should have an aspect ratio of 1.3
          base_aspect_ratio = 1.3
          )
```

## `draw_plot_label()` & `draw_label()`

```{r}
ggdraw(plot.mpg) + 
  draw_plot_label("A", size = 14) + 
  draw_label("DRAFT!", angle = 45, size = 80, alpha = .2)
```

## `ggdraw()`
```{r}
t <- (0:1000)/1000
spiral <- data.frame(x = .45+.55*t*cos(t*15), y = .55-.55*t*sin(t*15), t)
ggdraw(plot.mpg) + 
  geom_path(data = spiral, aes(x = x, y = y, colour = t), size = 6, alpha = .4)
```

## `draw_plot()`

Importantly, though, in all cases discussed so far, the main plot was below all other elements. Sometimes, you might want the plot on top. In this case, you can initialize an empty drawing canvas by calling ggdraw() without any parameters. You then place the plot by calling draw_plot().

```{r}
boxes <- data.frame(
  x = sample((0:33)/40, 40, replace = TRUE),
  y = sample((0:33)/40, 40, replace = TRUE)
)
# plot on top of annotations
ggdraw() + 
  geom_rect(data = boxes, aes(xmin = x, xmax = x + .15, ymin = y, ymax = y + .15),
            colour = "gray60", fill = "gray80") +
  draw_plot(plot.mpg) +
  draw_label("Plot is on top of the grey boxes", x = 1, y = 1,
            vjust = 1, hjust = 1, size = 10, fontface = 'bold')
# plot below annotations
ggdraw(plot.mpg) + 
  geom_rect(data = boxes, aes(xmin = x, xmax = x + .15, ymin = y, ymax = y + .15),
            colour = "gray60", fill = "gray80") + 
  draw_label("Plot is underneath the grey boxes", x = 1, y = 1,
            vjust = 1, hjust = 1, size = 10, fontface = 'bold')
```

```{r}
# plot.mpg and plot.diamonds were defined earlier
library(viridis)
ggdraw() +
  draw_plot(plot.diamonds + theme(legend.justification = "bottom"), 0, 0, 1, 1) +
  draw_plot(plot.mpg + scale_color_viridis(discrete = TRUE) + 
              theme(legend.justification = "top"), 0.5, 0.52, 0.5, 0.4) +
  draw_plot_label(c("A", "B"), c(0, 0.5), c(1, 0.92), size = 15)
```

## `draw_image()`

We can also combine plots and images, using the function draw_image(). This function, which requires the magick package to be installed, can take images in many different formats and combine them with ggplot2 plots. 

```{r}
p <- ggplot(iris, aes(x=Sepal.Length, fill=Species)) + geom_density(alpha = 0.7) + theme_cowplot()
ggdraw() +
  draw_image("http://jeroen.github.io/images/tiger.svg") +
  draw_plot(p)
```

```{r}
p <- ggplot(iris, aes(x = Sepal.Length, fill = Species)) + geom_density(alpha = 0.7)
p2 <- ggdraw() + draw_image("http://jeroen.github.io/images/tiger.svg", scale = 0.9)
plot_grid(p, p2, labels = "AUTO")
```

